A boundary-integral framework to simulate \\ viscous erosion of a porous medium

### 2018-04-10 docs/methods/erosion_methods.tex
NM

Analytical results for the case of a single eroding body provide a stringent benchmark for our simulation. In particular, by appealing to the principle of long-time uniform stress, we predict a front/rear corner of 102, which matches closely the value measured in the simulations. Scaling laws for the asymptotic rate of area and drag reduction also match the simulation.

Simulations of multiple eroding bodies reveals even more complex behavior. As in the single body case, we witness the formation of sharp corners, but not in locations that are easily predictable. Furthermore, bodies tend to form flat faces in places where there was initially near contact, which leads to the appearance of straight channels between bodies. The overall resistance of the porous network declines rapidly, which we attribute the channelization process.

>>>>

Analytical results for the case of a single eroding body provide a stringent benchmark for our simulation. In particular, by appealing to the principle of long-time uniform stress, we predict a front/rear corner of angle $102^{\circ}$, which matches closely the value measured in the simulations. Scaling laws for the asymptotic rate of area and drag reduction also match the simulation.

Simulations of multiple eroding bodies reveals even more complex behavior. As in the single body case, we witness the formation of sharp corners, but not in locations that are easily predictable. Furthermore, bodies tend to form flat faces in places where there was initially near contact, leading to the appearance of straight channels between bodies. The overall resistance of the porous network declines rapidly with erosion, which we attribute to the channelization process.

In work currently underway, we are using this method to examine more thoroughly how bulk and statistical properties of the porous medium change with erosion. We are particularly interested in the development of anisotropic permeability of the medium. Preliminary simulations show promise. We furthermore would like to investigate how the statistical distribution of bodies size, shape, and orientation changes over time. We hope to report on these topics soon.

As a longer term goal, we would like to include the effect of sedimentation to more faithfully capture the physics of a porous medium. Sedimentation requires overcoming a few challenges. First, the bodies must be mobile, as has been accomplished in previous work (cite). Second, contacts and overlap between bodies must be prevented. This second requirement has been recognized as quite a challenge, with many novel methods developed to treat it (CITE STUFF HERE). Incorporation of one or more of these schemes, will enable simulations of a porous medium undergoing simultaneous erosion and sedimentation.
